---
title: "analysis3exploration"
output: html_document
---


#Load libraries
```{r}
library(tidyverse)
library(dplyr)
library(broom)
library(ggplot2)
```

#Locate file
```{r}
data_location <- here::here("data","processed_data","processed_data.rds")
data <- readRDS(data_location)
```

Main continuous outcome: Body temperature (BodyTemp)
Main categorical outcome: Nausea
I am going to arbitrarily select other columns that may predict these outcomes.
Fatigue
SubjectiveFever
Pharyngitis
CoughYN (categorical)
SwollenLymphNodes

For each (important) variable, produce and print some numerical output (e.g. a table or some summary statistics numbers). Also, create a histogram or density plot.
or d
Important continuous variable: Body Temperature
```{r}

BodyTemp_table <- broom::tidy(summary(data$BodyTemp))

print(BodyTemp_table)

ggplot(data, aes(x=BodyTemp)) + geom_histogram() + ggtitle('Body Temperature Frequency Reports')

```
Looking at the histogram, Body Temperatures skews left, the mean looks to be around 99 degrees.


Important categorical variable: Nausea
```{r}
Nausea_table <- broom::tidy(summary(data$Nausea))

Nausea_table

ggplot(data, aes(x=Nausea)) + geom_bar() + ggtitle("Nausea Prevalence")

```
Boxplots for temperature and nausea reports

```{r}

data %>% ggplot(aes(x=Nausea, y=BodyTemp)) + geom_boxplot() +
  ggtitle("Nausea vs. Body Temperature")


```
Now I will pick a couple predictor values (I am picking these arbitrarily) and compare them to our main outcomes of interest. All of these are categorical.

* SubjectiveFever
* Vomit
* ChillsSweats
* Myalgia







Body temperature and Subjective fever
```{r}

data %>% ggplot(aes(x=SubjectiveFever, y=BodyTemp)) + geom_boxplot() +
  ggtitle("Body Temperature vs Subjective Fever)

```
Body temperature and Vomit
```{r}

data %>% ggplot(aes(x=Vomit, y=BodyTemp)) + geom_boxplot() + ggtitle("Body Temperatures and Vomit as Symptoms")

```

Body temperature and Chills/Sweats
```{r}

data %>% ggplot(aes(x=ChillsSweats, y=BodyTemp)) + geom_boxplot() +
  ggtitle("Body Temperature vs Chills/Sweats")

```

