---
title: "analysis3fitting"
output: html_document
---


## Load libraries
```{r}
library(tidyverse)
library(dplyr)
library(broom)
library(here)
library(modelr)
library(tidymodels)
```


Add code that does the following operations:

Loads cleaned data.
Fits a linear model to the continuous outcome using only the main predictor of interest.
Fits another linear model to the continuous outcome using all (important) predictors of interest.
Compares the model results for the model with just the main predictor and all predictors.
Fits a logistic model to the categorical outcome using only the main predictor of interest.
Fits another logistic model to the categorical outcome using all (important) predictors of interest.
Compares the model results for the categorical model with just the main predictor and all predictors.

Load cleaned data
```{r}
data_location <- here::here("data","processed_data","processed_data.rds")
data <- readRDS(data_location)
```


## Fits a linear model to the continuous outcome (Body temperature) using only the main predictor of interest (Runny nose).


1. Linear regression of Nausea and Body Temperature as an ANOVA because of the variables are categorical and continuous, respectively.
2. Training/estimating the linear model
```{r}
#1
lm_mod <- linear_reg() %>% set_engine("lm")

#2
lm_fit <- 
  lm_mod %>% 
  fit(BodyTemp ~ RunnyNose, data = data)
bodytemp_lm <- tidy(lm_fit)

```


## Fits another linear model to the continuous outcome using all (important) predictors of interest.

```{r}

lm_fit2 <- lm_mod %>% fit(BodyTemp ~ ., data = data)
important_predictors_lm <- tidy(lm_fit2)

```

## Compare Body Temperature (the main predictor) with all other predictors using an ANOVA.
```{r}
lm_compare <- anova(lm_fit$fit, lm_fit2$fit, test = "Chisq")
lm_compare_table <- tidy(lm_compare)
lm_compare_table
```

Looking at this comparison, we can see that we want to go with the lm_fit2 which looks at all predictors.

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## Now let's do the same thing, but with Nausea instead of body temperature

Set up logistical model to categorical:
```{r}

logistical_model <- logistic_mod <- logistic_reg() %>%
  set_engine("glm") %>%
  set_mode("classification")

```

##Fits another linear model to the categorical outcome using all (important) predictors of interest.

```{r}

log_fit <- logistical_model %>% fit(Nausea ~ RunnyNose, data = data)
nausea_lm <- tidy(log_fit)
nausea_lm

```

## Compare Nausea (the main predictor) with all other predictors using an ANOVA.
```{r}

log_fit2 <- logistical_model %>%
  fit(Nausea ~ ., data = data)



log_compare <- anova(log_fit$fit, log_fit2$fit, test = "Chisq")
log_compare_table <- tidy(log_compare)
log_compare_table
```
Looking at the ANOVA results, we can see that we want to go with the log_fit2 which looks at all predictors.


## Saving our results:
```{r}
saveRDS(lm_compare_table, file = here("results", "linearmodeltable.rds"))
saveRDS(log_compare_table, file = here("results", "logisticmodeltable.rds"))

```





